% ==========================================
% Thesis Report - Organization ( brods1 )
% ==========================================

\chapter{Organisation}

\section{Team}
The project team consists of three students: Brigitte Hulliger, Jonas Walti and Stefan Broder. All of us study Information Technology at the \gls{bfhti} in Biel. We are in the last semester of our bachelor degree course. Our main topic is Computer Perception and Virtual Reality in which we were educated for the last three semesters.

The bachelor thesis was supervised by Michael Luggen, an assistent and former student of the BFH, and Prof. K\"unzler, lecturer and researcher in \gls{cpvr}. 

\section{Wiki}
To share and exchange common project information within the thesis group, it turned out to be very helpful to use a wiki. The wiki can be found on \href{https://wiki.brooper.dyndns.org}{https://wiki.brooper.dyndns.org}. The wiki page runs on a private server from one of the students. Hence, it is not guaranteed to be accessible while you read this.

\section{Subversion}
To enable development on common sources it was vital to use some kind of version control. Therefore, we decided to use subversion. \gls{bfhti} runs a subversion server which can be used for thesis projects by students. We used version control for our source code as well as for our documentation.

Our repository can be checked out on \href{https://svn.bfh.ch/repos/projects/thesis09\_cave}{https://svn.bfh.ch/repos/projects/thesis09\_cave}. You need to have a valid and authorised \gls{bfhti} account for that matter.
