% ==========================================
% Thesis Report - Procedure ( hullb2 )
% ==========================================
\chapter{Procedure}

Since this project was a research project that did not promise a working outcome, part of the project was to find out how to find a solution that satisfies the requirements. 
A few prerequisits were given before the project started, one of them Equalizer. A former project at the \gls{bfhti} did already compare the two scene graph technologies \gls{osg} and \gls{ogre}. Therefore the usage of one of these technologies was given as a requirement too. 

Part of the hardware used for the project was existing. The \gls{cave} was configured with a setup consisting of six render clients. The server that was already setup in the \gls{cave} was taboo since it must always be available for other demos. We did not know if the six render clients were really set up for our project or not. 

This was the point of departure in our project. Therefore, the first task of all we had to solve was to bring some system in the upcoming work.
Though we all agreed that it does not make sense to set an official milestone each week, we decided to define some kind of internal milestones in weekly steps. 

The next organisational decision we made was, that we meet twice a week to work together on the project. On Thursdays all day long and on Fridays for the morning. Therefore it was necessary to have a workplace at school.

After the first few weeks, we decided to devide the project in three parts, one part for each team member.

\begin{table}[H]
	\centering
	\begin{tabular}{|p{0.1\textwidth}|p{0.2\textwidth}|p{0.15\textwidth}|p{0.4\textwidth}|} 
		\hline \bfseries abbr. & \bfseries Name & \bfseries speciality & \bfseries comment \\
		\hline
		\hline hullb2 & Brigitte Hulliger & Equalizer & Equalizer configuration and setups \\
		\hline waltj3 & Jonas Walti & Framework & Implementation of the framework with respect to eqOSG \\
		\hline brods1 & Stefan Broder & Hardware Setup & Hardware Setup for CAVE \\
		\hline
	\end{tabular}
	\caption{Team members and their specialities in the project}
\end{table}

Our internal milestones are listed in \ref{sec:appendixWorklog}. At the beginning of the project these milestones were only vaguely worked out since e did not know what we will have to do until the end. But with progressing weeks, this plan got more detailed.


